\textbf{NBA Party}

### 2017-07-08 cardinal_analytx_presentation/nightlife_and_sports.tex
Removed demeaned.rebounds.per.minute, added section on interpreting logistic regression results.

\begin{frame}   
  \frametitle{Continuous measure of party (NBA)}
  \centering \includegraphics[scale=0.3]{../writing/Party_by_Team_Location} 
\end{frame}

@@

@@

\begin{frame}   
  \frametitle{Continuous measure of party (MLB)}
  \centering \includegraphics[scale=0.3]{../writing/Party_by_Team_Location_mlb}   
\end{frame}

@@

\begin{frame}   \frametitle{Analysis: rebounds}
  \begin{itemize}     \item For each player and each game, we calculate the number of rebounds obtained per-minute of game-play
    \item From each observation, we subtract the player's average number of rebounds per minute taken across the entire season.
    \item We then run a linear regression explaining demeaned rebounds as a function of 
      nightlife visitation and other features describing player fatigue.   \end{itemize} \end{frame}

\begin{frame}   \frametitle{Results: rebounds}
  \centering
  \tiny{ % m2
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Demeanead Rebounds Per Minute \\  \hline \\[-1.8ex]   Continuous party measure & $-$0.004$^{*}$ \\    & (0.002) \\    & \\   Lag change in possessions & 0.00002 \\    & (0.0001) \\    & \\   Logged travel distance & 0.001 \\    & (0.001) \\    & \\   Number hours since last game & 0.00002 \\    & (0.00002) \\    & \\   Constant & $-$0.007 \\    & (0.004) \\    & \\  \hline \\[-1.8ex]  Observations & 40,684 \\  R$^{2}$ & 0.0003 \\  Adjusted R$^{2}$ & 0.0002 \\  Residual Std. Error & 0.104 (df = 40679) \\  F Statistic & 2.696$^{**}$ (df = 4; 40679) \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  } \end{frame}

>>>>

\begin{frame}   
  \frametitle{Continuous measure of party}
  \centering \includegraphics[scale=0.3]{../writing/Party_by_Team_Location} 
\end{frame}

@@

\begin{frame}   \frametitle{Interpreting our results}
  Let's consider the simplest model, where $Y_i | X \sim \textrm{Bern}(p)$, i.e.
  $\Pr(Y_i = y | X) = p^{y} (1-p)^{1-y}$. Using a generalized linear model,
  we fit a linear predictor to a transformation of the expected value of our
  variable of interest. I.e.
  \[
    \textrm{logit} \left( \mathbb E[Y_i | X]\right) = \textrm{logit} \left(p\right) = \ln \left( \frac{p}{1-p}\right) = X \beta.
  \]
  So, we interpret our regression coefficient as follows: visiting LA or NY within
  24 hours of another game corresponds to being $e^{\beta_1} \approx e^{-0.55} \approx \frac{3}{5}$
  as likely to meet the spread, all other factors held constant. 
\end{frame}

@@

% \begin{frame}   
%   \frametitle{Continuous measure of party (MLB)}
%   \centering \includegraphics[scale=0.3]{../writing/Party_by_Team_Location_mlb}   
% \end{frame}

@@

% \begin{frame}   \frametitle{Analysis: rebounds}
%   \begin{itemize}     \item For each player and each game, we calculate the % number of rebounds obtained per-minute of game-play
%     \item From each observation, we subtract the player's average number of % rebounds per minute taken across the entire season.
%     \item We then run a linear regression explaining demeaned rebounds as a % function of 
%       nightlife visitation and other features describing player fatigue.   % \end{itemize} \end{frame}

% \begin{frame}   \frametitle{Results: rebounds}
%   \centering
%   \tiny{ % m2
% \begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & % \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & % Demeanead Rebounds Per Minute \\  \hline \\[-1.8ex]   Continuous party measure & % $-$0.004$^{*}$ \\    & (0.002) \\    & \\   Lag change in possessions & 0.00002 % \\    & (0.0001) \\    & \\   Logged travel distance & 0.001 \\    & (0.001) \\    % & \\   Number hours since last game & 0.00002 \\    & (0.00002) \\    & \\   % Constant & $-$0.007 \\    & (0.004) \\    & \\  \hline \\[-1.8ex]  Observations % & 40,684 \\  R$^{2}$ & 0.0003 \\  Adjusted R$^{2}$ & 0.0002 \\  Residual Std. % Error & 0.104 (df = 40679) \\  F Statistic & 2.696$^{**}$ (df = 4; 40679) \\  % \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; % $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  } \end{frame}
